Analysis of Climate Sensitivity using HadAM3

### 2014-04-27 article.tex
Structure/layout of results section.

\newif\ifsubsection
\subsectiontrue
%\subsectionfalse

@@

\ifsubsection
\subsection{General Circulation Models}
\fi
% Explain GCMs.
To study the release of \ce{CO2} into the atmosphere, General Circulation Models (GCMs) can be employed. These model the various processes that make up the Earth's dynamic behaviour such as the movements of the atmosphere or the oceans. They typically model these processes using a grid that spans the surface of the Earth, with variables such as temperature and pressure represented at each grid cell. The first GCMs just modelled the atmosphere (TODO: cite), but as they have developed they have gone on to encompass more of the Earth's systems, such as the oceans, the cryosphere and the biosphere. Indeed, certain large scale climatic modes such as the El ni{\~n}o Southern Oscillation (ENSO) can only be adequately modelled when the coupling between the atmosphere and the ocean is included (TODO: cite Neelin + others?).

@@

\ifsubsection
\subsection{Radiative forcing and feedbacks}
\fi
% Talk about Radiative Forcing and feedbacks.
% As \ce{CO2} increases, the incoming short-wave radiation reaching the Earth's surface is largely unaffected. However, more of the outgoing long-wave radiation emitted by the surface is absorbed by the atmosphere, which leads to the atmosphere heating up. As it heats, it too emits more long-wave radiation, but it does so isotropically, so an equal amount of this radiation is directed back towards the Earth's surface as well as into space. 
Any imbalance between the net incoming short-wave solar radiation and the net outgoing long-wave radiation from the Earth is know as a Radiative Forcing (RF), which is measure in \SI{}{W.m^{-2}}. A positive RF will tend to increase the temperature of the planet, whereas a negative one will decrease it. As the amount of \ce{CO2} in the increases, it absorbs more of the outgoing long-wave radiation, which leads to a RF. Similar RFs can be defined for other GHGs such as Methane.

@@

% Talk about regional effects and why they're important.
\ifsubsection
\subsection{Regional effects of increased \ce{CO2}}
\fi
% experienced at a regional level.
A \SI{2}{K} rise in global surface temperatures cannot be directly experienced by humans; it is on a regional scale that humans will be affected. It is therefore important that the regional effects of increased \ce{CO2} are understood, so as plans can be put in place to mitigate the worst of these effects and changes can be made ahead of time to adapt to the changing environment. The predicted regional effects over South America are detailed in AR5 (TODO: cite). Two findings from that report will be examined using the HadAM3 model:
\begin{itemize}
    \item ``it is \textit{very likely} temperatures will increase over the whole continent, with greatest warming projected in southern Amazonia.''
    \item ``It is very likely that less rainfall will occur in eastern Amazonia, northeast and eastern Brazil during the dry season. However, in the rainy season there is medium confidence in the precipitation changes over these regions.''
\end{itemize}

@@

\section{Results}

@@

@@

@@

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/corr}
    \caption{Caption.}
    \label{fig:corr}
\end{figure}

\section{Discussion}

>>>>

@@

\subsection{General Circulation Models}
% Explain GCMs.
To study the release of \ce{CO2} into the atmosphere, General Circulation Models (GCMs) can be employed. These model the various processes that make up the Earth's dynamic behaviour such as the movements of the atmosphere or the oceans. They typically model these processes using a grid that spans the surface of the Earth, with variables such as temperature and pressure represented at each grid cell. The first GCMs just modelled the atmosphere (TODO: cite), but as they have developed they have gone on to encompass more of the Earth's systems, such as the oceans, the cryosphere and the biosphere. Indeed, certain large scale climatic modes such as the El ni{\~n}o Southern Oscillation (ENSO) can only be adequately modelled when the coupling between the atmosphere and the ocean is included (TODO: cite Neelin + others?).

@@

\subsection{Radiative forcing and feedbacks}
% Talk about Radiative Forcing and feedbacks.
% As \ce{CO2} increases, the incoming short-wave radiation reaching the Earth's surface is largely unaffected. However, more of the outgoing long-wave radiation emitted by the surface is absorbed by the atmosphere, which leads to the atmosphere heating up. As it heats, it too emits more long-wave radiation, but it does so isotropically, so an equal amount of this radiation is directed back towards the Earth's surface as well as into space. 
Any imbalance between the net incoming short-wave solar radiation and the net outgoing long-wave radiation from the Earth is know as a Radiative Forcing (RF), which is measure in \SI{}{W.m^{-2}}. A positive RF will tend to increase the temperature of the planet, whereas a negative one will decrease it. As the amount of \ce{CO2} in the increases, it absorbs more of the outgoing long-wave radiation, which leads to a RF. Similar RFs can be defined for other GHGs such as Methane.

@@

% Talk about regional effects and why they're important.
\subsection{Regional effects of increased \ce{CO2}}
% experienced at a regional level.
A \SI{2}{K} rise in global surface temperatures cannot be directly experienced by humans; it is on a regional scale that humans will be affected. It is therefore important that the regional effects of increased \ce{CO2} are understood, so as plans can be put in place to mitigate the worst of these effects and changes can be made ahead of time to adapt to the changing environment. The predicted regional effects over South America are detailed in AR5 (TODO: cite). Two findings from that report will be examined using the HadAM3 model:
\begin{itemize}
    \item ``it is \textit{very likely} temperatures will increase over the whole continent, with greatest warming projected in southern Amazonia.''
    \item ``It is very likely that less rainfall will occur in eastern Amazonia, northeast and eastern Brazil during the dry season. However, in the rainy season there is medium confidence in the precipitation changes over these regions.''
\end{itemize}

@@

\newpage
\section{Results}

\subsection{Calculation of TCR and $CS_{\ce{CO2}}$}

\subsection{Global changes between 1\%py and control scenarios}

Discussion about Figure \ref{fig:global_temp_precip} to go here.

@@

\newpage
\subsection{Seasonal changes in South America}

Discussion about Figure \ref{fig:sa_seasonal} to go here.

@@

\newpage
\subsection{Interdependence of variables in South America}

Discussion about Figure \ref{fig:sa_diff} to go here.

@@

\newpage

Paragraph about Figure \ref{fig:corr} plots.
\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/corr}
    \caption{Caption.}
    \label{fig:corr}
\end{figure}

\newpage
\section{Discussion}
